The pollination trade-off

### 2018-10-16 paper/manuscript.Rmd
Add hugo's address
Close #28
Add Fer's Hugo's and Daniel's awknowledgements
Issue #29

^2^ Hugo's address

@@

>>>>

^2^ Centro de Recursos Naturales Renovables de las Zonas Semiáridas, CONICET, Camino de la Carrindanga Km. 7, 8000 Bahía Blanca, Argentina

@@

# Acknowledgements

We thank  Cátedra de Botánica General, Facultad de Agronomía, Universidad de Buenos Aires. 
The Agrasar and Bordeu families, and the University of Buenos Aires, for logistical support and permission to conduct this study at estancias Anquilóo, Las Chilcas and San Claudio, respectively.  
Field work was supported by grants PICT 08–12504 and 0851. 
EFC acknowledges the support from the University of Canterbury Doctoral Scholarship, the University of Canterbury Meadow Mushrooms Postgraduate Scholarship, and a New Zealand International Doctoral Research Scholarship.
DBS acknowledges the support of a Marsden Fast-Start grant and a Rutherford Discovery Fellowship, administered by the Royal Society Te Aparangi.
